DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car

### 2017-10-05 paper/intro.tex
Add draft summary of findings to intro

% how we trained (maybe moved to a later section)
We apply a standard imitation learning methodology to train the cat to
follow tracks on the ground. We collect data for
training and validation by manually
controlling the RC car and recording the vision (from the webcam
mounted on the RC-car) and the human control inputs. We then train the
network offline using the collected data on a desktop computer, which
equips a NVIDIA GTX 1060 GPU. Finally, the trained network is copied
back to the Raspberry Pi, which is then used to perform interference
operations---locally on the Pi---in the car's main control loop in
real-time. For real-time control, each inference operation must
be completed within the desired control period. (e.g., 50ms period for
20Hz control frequency.)
% how we evaluated (in terms real-time performance)

% what are our findings?
\fixme{TBD: Summary of our findings}

>>>>

% how we trained (maybe moved to a later section)
We apply a standard imitation learning methodology to train the car to
follow tracks on the ground. We collect data for
training and validation by manually
controlling the RC car and recording the vision (from the webcam
mounted on the RC-car) and the human control inputs. We then train the
network offline using the collected data on a desktop computer, which
equips a NVIDIA GTX 1060 GPU. Finally, the trained network is copied
back to the Raspberry Pi, which is then used to perform interference
operations---locally on the Pi---in the car's main control loop in
real-time. For real-time control, each inference operation must
be completed within the desired control period. (e.g., 50ms period for
20Hz control frequency.)
% how we evaluated (in terms real-time performance)

% what are our findings?
From our experiments, we discover that the DeepPicar is capable of 
completing control loops in under 50 ms, or 20 hz, and can do so 
almost 99\% of the time. The number of cores used by the platform has 
an unexpectedly low impact on its performance, only decreasing the 
control loop times by 30\% when using 4 cores instead of 1.  Our 
platform shows the potential to run multiple neural network models 
simultaneously, as there are no indications of direct interference 
between them. Instead, we show that memory intensive co-runners can 
be detrimental to the real-time performance of the DeepPicar. 
Finally, while we find that the Raspberry Pi 3 takes longer to 
complete control loops when compared to other embedded computing 
platforms, namely the Intel UP Board and the NVIDIA Tegra TX2, we 
still conclude that the Pi 3 is a viable option for autonomous 
vehicle research.
